\documentclass[11pt, a4paper, sans]{moderncv}

\usepackage[english]{babel}
\usepackage[margin=20mm,top=15mm,bottom=15mm]{geometry}

\input{common.tex}

%%%%%%%%%%%%%%%%%%%%
% Basic infos
%%%%%%%%%%%%%%%%%%%%

%\address{PLACEHOLDER_ADDRESS1}{PLACEHOLDER_ADDRESS2}
PLACEHOLDER_MOBILE_NUMBER  % if \mobile{} is empty, the phone logo still shows up
\email{PLACEHOLDER_EMAIL}
\homepage{PLACEHOLDER_HOMEPAGE}
%\social[github]{Nodraak}
%\extrainfo{PLACEHOLDER_EXTRAINFO} % birthday

%%%%%%%%%%%%%%%%%%%%
% Version and page number
%%%%%%%%%%%%%%%%%%%%

\cfoot{\vspace{-15pt}\small\itshape\textcolor{gray}{
    Page \thepage\ of \pageref{LastPage}
    - Version PLACEHOLDER_VERSION \input{|"git rev-parse --short HEAD"}\input{|"git log -1 --date=short | grep Date | cut -b 9-"}
}}

%%%%%%%%%%%%%%%%%%%%
% Content - First page
%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\large
    Adrien is a software and electronics engineer, with an expertise in embedded
    and critical systems.
    He is interested in robots, launchers and inter-planetary probes.
    He cares about code quality, automation and open source software.
}
\makecvtitle

%%%%%%%%%%%%%%%%%%%%
\nodSection{Work Experience}
%%%%%%%%%%%%%%%%%%%%

\setlength{\hintscolumnwidth}{30mm}

\nodCvItem
    {PTS}
    {Since 2021-01}
    {Berlin, Germany}
    {Software Engineer - ASTRIS kickstage}
    {
        \nodItem{\textit{%
            The ASTRIS kickstage is a 5 tons spacecraft developed by ArianeGroup to be flown on Ariane 6 to provide additional capabilities and flexibility to payloads.
            In collaboration with ArianeGroup, \textbf{PTS designed the full avionics of ASTRIS} up to PDR.
            The PTS developed avionics covered the \textbf{electronics of the OBC}, the power, data acquisition and valves and pyros control subsystems, as well the \textbf{low-level software of the OBC, and complete software of the other subsystems}.
        }}
        \nodItem{Within the software team, I contributed to the following topics:}
        \nodItem{\textbf{Architecture and design}: requirements flow down, functional architecture decomposition, design of the CANopen-based internal bus of the avionics.}
        \nodItem{\textbf{Documentation} (following ECSS standard): software unit and validation test plans (SUITP / SVTP), software design document (SDD) and interface control documents (ICD) ; With a focus on the IOs drivers (UART, CAN, SPI), Datapool and Telemetry pipeline.}
        \nodItem{\textbf{Implementation and integration}: ARM \si{\micro}controllers BSP (Zynq 7020, SmartFusion2), RTOS (RTEMS), drivers (UART, CAN, SPI). Version control and CI (Git and GitLab), maintaining three execution targets for different levels of tests (x86/Linux, ARM/QEMU, ARM/Zynq), code coverage (GCOV), static analysis (Cppcheck, SonarQube, MISRA), unit tests (VectorCast).}
    }
\nodCvItem
    {PTS}
    {Since 2021-01}
    {Berlin, Germany}
    {Software Engineer - CLAM (IoT solution for logistics)}
    {
        \nodItem{\textit{%
            CLAM is a monitoring and optimization solution for logistics: it provides the position, temperature, humidity, etc of the container or truck, as well as its loading level.
        }}
        \nodItem{\textbf{As the main responsible for the software}, I researched, designed and developed both the embedded software running in the containers and the backend to administrate the units and visualize the data.}
        \nodItem{\textbf{Embedded software:} ESP32, GSM and GNSS modules, distance sensor (VL53), environmental sensors (temperature, humidity), IMU.}
        \nodItem{\textbf{Backend software:} Django, SQLite, Grafana, Nginx.}
        \nodItem{\textbf{Electronics:} prototype PCB layout, routing and soldering, testing.}
    }

\nodCvItem
    {GMV}
    {2019-2020}
    {Madrid, Spain}
    {Software Engineer - Exomars}
    {
        \nodItem{\textbf{Exomars rover}: as the \textbf{main technical responsible}, I developed and validated a middleware to interface the autonomous navigation libraries (CNES) with the rover platform (Airbus UK). During development, I configured a \textbf{CI pipeline to ensure high quality code and up to date reports}: running automated test on x86 and SPARC, tracking coverage and static analysis results, and automatically generating documentation.}
        \nodItem{\textbf{Exomars cruise and descent modules}: I \textbf{helped in the development of the GNC}: coding, bug fixes, testing, validation, and improvement of the software quality metrics.}
        \nodItem{\textbf{Skills:} programming (embedded C, Python), unit and integration testing (VectorCast, Tsim, Leon 2 FT on Rasta board), quality tools (Cppcheck, Gitlab CI, code coverage), software development standards (MISRA-C, ECSS-40B).}
    }

%%%%%%%%%%%%%%%%%%%%
% Content - Second page
%%%%%%%%%%%%%%%%%%%%

\newpage
\title{}
\makecvtitle

\nodCvItem
    {ECE Paris}
    {2017-2018}
    {Paris, France}
    {Project Leader (Student) - Smallsat ECE3Sat}
    {
        \nodItem{In collaboration with a team of 25 people, I designed and built a \textbf{nano satellite} in order to study a new de-orbit technique using Earth's magnetic field.}
        \nodItem{
            \textbf{I managed the team} (5 people) responsible for the satellite architecture and the on-board computer.
            \textbf{We implemented the on-board communication bus} with CAN and ASN.1 to ensure a reliable communication between the subsystems.
        }
        \nodItem{\textbf{Skills:} distributed architecture design, sizing and \si{\micro}controllers choice, team management and coordination.}
    }

\nodCvItem
    {ECE Paris}
    {2016-2017}
    {Paris, France}
    {Software Engineer (Student) - Robot Gali X}
    {
        \nodItem{With a team of 5, \textbf{we built an autonomous robot} for the French Robotic cup.}
        \nodItem{\textbf{In charge of the software}, I designed a \textbf{distributed architecture} to allow easier reuse for the future robots.}
        \nodItem{I implemented a \textbf{telemetry GUI} to monitor the robot status and a \textbf{simulator} to assess the performances (recompilation of ARM code for execution on x86).}
        \nodItem{\textbf{Skills:} embedded C/C++, Python (telemetry GUI, software-in-the-loop simulation), drivers for CAN bus and other peripherals, ARM \si{\micro}controllers, Git.}
        \nodItem{Video demo and source code available at \normalfont{\url{https://cv.nodraak.fr}}}
    }

%%%%%%%%%%%%%%%%%%%%
\nodSection{Education}
%%%%%%%%%%%%%%%%%%%%

\setlength{\hintscolumnwidth}{30mm}

\subsection{Degrees}

\cventry{\centerline{2018}}{Advanced Master}{TAS Astro: space systems design}{}{}{ISAE-Supaero - Toulouse, France}
\cventry{2013 - 2018}{Engineering Degree}{Majoring in embedded systems}{}{}{ECE Paris - Paris, France}
\cventry{2015 - 2016}{Bachelor of Science}{Electronics \& IT}{}{}{Aalborg University - Aalborg, Denmark}

\subsection{Languages}

\cventry{French}{Native}{}{}{}{}
\cventry{English}{Fluent (C2)}{}{}{}{}
\cventry{German}{Conversational (B1)}{}{}{}{}
\cventry{Spanish}{Conversational (B1)}{}{}{}{}

%%%%%%%%%%%%%%%%%%%%
\nodSection{Hobbies}
%%%%%%%%%%%%%%%%%%%%

\setlength{\hintscolumnwidth}{30mm}

\cvitem{Writing}{\url{https://blog.nodraak.fr}}
\cvitem{Tourism}{Museums and cities}
\cvitem{Sports}{Running (HM: 1h29), swing dancing, roller/ice skating}
\cvitem{Learning and making}{Software and robotics projects - Recently: learning Rust lang}
\cvitem{Playing}{Kerbal Space Program}

\end{document}
